\begin{abstract}
\paragraph{}
For considerable time, therapist have been researching the possibility to give social phobic patients a treatment with \gls{avatar}s. For so far, this has been done in a lab on a university or hospital. To reduce costs new research is investigating the possibility to bring the treatment to the patients home by introducing an \gls{eCoach}. The \gls{eCoach} should take over most of the tasks of the therapist. These include motivating, helping and informing the patient, reflecting on exposure sessions, monitoring treatment progress and giving feedback. 
\paragraph{}
A plan has been made to develop the \gls{eCoach} system. In order of priority the following system components will be developed: anxiety questionnaire, progress overview, communication server, progress reflection, personalized avatar, suggestions from avatar, outside events discussing. 
\paragraph{}
To ensure the quality of the shipped product, a clear definition of 'done' is given. To be done, a feature has to be tested with unit tests and integration tests. The performance must be tested, the code must be sufficiently commented, documented and reviewed by automatic tools and peers. A sprint is completed when the backlog is up to date, the code is merged, tagged and refactored for maintainability, the \gls{UML} diagrams are updated, and has been approved by the product owner. A release is done when is has been thoroughly tested, both automatic and manually, and has been approved by the product owner.
\end{abstract}
