\chapter{Definition of Done}

The definition of done (DoD) is a guideline to review the work that has been done and if it will be acceptable for release. To have a definition of what is done and what is not makes it easy for team members to correct each others work, but also to check if your own work is ready.
This section is divided in three parts. The first will describe a definition of done for a feature or a user-story. These are the product backlog items that are due in one sprint. The next part is a definition of done for a whole sprint. This focuses mainly on the integration of the different features. The last is the definition of done for a release. The release has most of the features implemented and is potentially ready to ship.

\section{DoD for a Feature}

\begin{itemize}
\item Unit tests written
\item Code complete
\item Unit tests are executed and passed
\item Integration tested
\item Performance tested
\item Code sufficiently commented and documented
\item Code is reviewed with automatic tools or by peers
\end{itemize}

\section{DoD for a Sprint}
\begin{itemize}
\item All features and user-stories that are not done added to product backlog
\item New code is properly merged and tagged
\item Code is re-factored to make it maintainable and expandable
\item \gls{UML} diagrams are updated
\item Sprint has product owner approval
\end{itemize}

\section{DoD for a Release}
\begin{itemize}
\item Thoroughly automatically tested
\item Manually tested
\item Product owner approval
\item Product is properly packaged
\end{itemize}