\chapter{Product backlog}

\section{User stories of features}
\begin{itemize}
\item As a therapist I want to monitor the patient’s progress
\item As a therapist I want to gain information about the patient via a questionnaire
\item As a patient I want to communicate with my therapist
\item As a therapist I want to communicate with my patients
\item As a therapist I want to retrieve files of the patient’s progress
\item As a therapist I want the avatar to talk with the patients about their social events outside of the therapy
\item As a patient a clear overview of my progress in form of graphs, tables and animations
\item As a therapist I want an overview of my patients 
\item As a patient I want to be motivated by the avatar
\item As a patient I want tips and suggestions from the avatar based on my progress
\item As a patient I want to have clear instructions what I have to for the next session based on the previous session.
\item As a therapist I want the avatar to be able to adapt the way it gives feedback to the patient
\item As a patient I want the avatar to reflect results with me and say what I have done well and where I need to improve.
\end{itemize}
 
\section{User stories of defects}
There are no user stories of defects at this time.

\section{User stories of technical improvements}
There are no user stories of technical improvements at this time.

\section{User stories of know-how acquisition}
\begin{itemize}
\item As a developer I need to fully understand what social phobia means.
\item As a developer I need to know communicate with social phobic patients.
\item As a developer I need to what kind of situations social phobic patients fear.
\item As a developer I need to know program an avatar.
\end{itemize}
\section{Initial release plan}